Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data

### 2021-07-27 Manuscript/00-main.Rmd
Creating Result Tables

library(knitr)
library(targets)
library(here)

tar_load(intro_path)
tar_load(method_path)
tar_load(sim_path)
tar_load(real_data_path)
tar_load(disc_path)
```

>>>>

library(knitr)
library(targets)
library(here)
library(xtable)

tar_load(intro_path)
tar_load(method_path)
tar_load(sim_path)
tar_load(real_data_path)
tar_load(disc_path)

tar_load(tab_binom)
tar_load(tab_gaus)
```

### 2021-07-27 Manuscript/SS_GAM.tex
Creating Result Tables

@@

\includegraphics{SS_GAM_files/figure-latex/unnamed-chunk-7-1.pdf}

@@

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{rrllllll}
  \hline
 & p & bglm\_spline\_de & blasso\_spline & cosso & acosso & mgcv & SB\_GAM \\ 
  \hline
1 & 4.00 & 0.94 (0.01) & 0.89 (0.04) & 0.90 (0.02) & 0.90 (0.02) & 0.94 (0.01) & 0.93 (0.01) \\ 
  2 & 10.00 & 0.93 (0.01) & 0.87 (0.03) & 0.87 (0.03) & 0.85 (0.03) & 0.92 (0.04) & 0.92 (0.01) \\ 
  3 & 50.00 & 0.92 (0.01) & 0.87 (0.02) & 0.83 (0.02) & 0.83 (0.02) & 0.76 (0.04) & 0.92 (0.01) \\ 
  4 & 200.00 & 0.88 (0.01) & 0.86 (0.02) & 0.81 (0.06) & 0.81 (0.08) & NaN (NA) & 0.92 (0.01) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample area under the curve measure over for binomial outcome over 50 iterations} 
\label{tab:bin_auc}
\end{table}

@@

@@

\includegraphics{SS_GAM_files/figure-latex/unnamed-chunk-10-1.pdf}
